Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-06-11 paper/long_version.tex
Auto Update from local Sharelatex

\begin{table}
	\caption{Kung Faux Pandas data synthesis plugin timings (seconds)}
	\label{timing_results}
	\centering
	\begin{tabular}{l c c c c c}
		\toprule 
		Method & 10 rows & 100 rows & 1000 rows & 10000 rows & 100000 rows\\ 
		\midrule 
		Trivial & 2.5e-06 & 2.25e-06 & 2.27e-06 & 2.23e-06 & 2.16e06 \\ 
		KDE & x.y (1.04) &  & x.y (1.04) &  &  \\ 
		DS Correlated & x.y (1.04) &  &  & x.y (1.04) &  \\ 
		DS Correlated w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\ 
		DS Independent & x.y (1.04) &  &  &  &  \\ 
		DS Independent w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\
		\midrule
	\end{tabular}
\end{table}

>>>>

\begin{table}
	\caption{Kung Faux Pandas data synthesis plugin timings (mean seconds)}
	\label{timing_results}
	\centering
	\begin{tabular}{l c c c c c}
		\toprule 
		Method & 10 rows & 100 rows & 1000 rows & 10000 rows & 100000 rows\\ 
		\midrule 
		Trivial & 2.5e-06 & 2.25e-06 & 2.27e-06 & 2.23e-06 & 2.16e06 \\ 
		KDE & 0.086 & 0.079 & 0.074 & 0.074 & 0.122 \\ 
		DS Correlated & x.y (1.04) &  &  & x.y (1.04) &  \\ 
		DS Correlated w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\ 
		DS Independent & x.y (1.04) &  &  &  &  \\ 
		DS Independent w/Config & x.y (1.04) &  &  &  & x.y (1.04) \\
		\midrule
	\end{tabular}
\end{table}
